Response to reviewers

### 2022-02-17 response/response1.Rmd
done with response for now
updated response

@@

@@

* **NEED HELP** We have added more explanation on the process used to decide on the threshold.

@@

* NEED HELP We are really not sue what this refers to.

>>>>

* Similar comment to this is addressed above.

* Thank you, we have changed from "M estimation" to "iteratively reweighted least squares".

@@

* **NEED HELP** The paper has been fixed so that male/female is used consistently. We have also rewritten the paragraph to focus on the survey questions and shortcomings.

@@

@@

* NEED HELP We are really not sure what this refers to.
